---
title: "Site Selection"
author: "Derek Corcoran"
date: "`r format(Sys.time(), '%d/%m, %Y')`"
output:
  ioslides_presentation:
    widescreen: true
    incremental: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, tidy = TRUE, tidy.opts = list(width.cutoff = 50))
library(tidyverse)
library(broom)
library(kableExtra)
library(knitr)
library(plotly)
library(crosstalk)
library(leaflet)
library(terra)
library(sf)
options("kableExtra.html.bsTable" = T)
```

## Candidate plots


* 100,594 sites
* Includes NOVANA, Biowide and paragraph 3

## Filter by Dry nature

```{r}
DryNaturePlots <- readRDS("DryNaturePlot.rds")  %>%
  sf::st_transform('+proj=longlat +datum=WGS84')
```

* only `r prettyNum(nrow(DryNaturePlots), big.mark = ",")` of the plots are dry Nature

```{r}
leaflet(DryNaturePlots) %>% 
  addTiles() %>% 
  addCircleMarkers(clusterOptions = markerClusterOptions())
```

## Select by higher diversity

* Select highest (Diversity, species richness and Artscore)
* Ensure 5 km minimum distance to closest neighbour
* Compute 
    + Patch area [ha]
    + Mean proportion of Dry Nature (500, 1000, 5000)
    + CV of dry nature
* Only for habitats with more than 5 occurrences

## Proportion vs CV

```{r}
Summary <- readRDS("Summary_2500.rds")
MoreThanFive <- Summary %>%
  as.data.frame() %>%
  dplyr::filter(total_nature_cv < median(Summary$total_nature_cv)) %>% 
  replace(is.na(.), 0) %>%
  group_by(habitat) %>%
  summarise(n = n()) %>%
  dplyr::filter(n > 5) %>%
  arrange(desc(n))


G <- ggplot(Summary, aes(x = total_nature_mean, y = total_nature_cv)) + geom_point() +
  theme_bw() +
  geom_hline(yintercept = median(Summary$total_nature_cv), lty = 2, color = "red") +
  labs(y = "Coefficient of variation of Total Nature", x = "Average proportion of Total Nature")

ggplotly(G)
```

## Nature types

```{r}
Summary2 <- Summary %>% dplyr::filter(habitat %in% MoreThanFive$habitat, total_nature_cv < median(Summary$total_nature_cv))

G2 <-  ggplot(Summary2, aes(x = reorder(habitat, total_nature_mean), y = total_nature_mean)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Habitat", y = "Average proportion of total nature")

ggplotly(G2)
```



## Candidate points

```{r}
Candidates <- readRDS("CandidatesDryCont_2500.rds") %>% ungroup() %>% dplyr::filter(habitat %in% MoreThanFive$habitat) %>% dplyr::select("akt_id", "year", "habitat", "Patch_Size", "sp_richness", "total_nature_mean", "total_nature_cv",
"nature_dry_mean", "nature_dry_cv", "lake_mean", "lake_cv","forest_mean", "forest_cv", "agriculture_intensive_temporary_crops_mean", "agriculture_intensive_temporary_crops_cv", 
"agriculture_intensive_permanent_crops_mean",
"agriculture_intensive_permanent_crops_cv", "Tempcont", "lon", "lat")
```


* Among the most common habitats (More than five)
* Coefficient of variation lower than `r round(median(Summary$total_nature_cv),2)`
* Total number `r nrow(Candidates)`

## Temporal continuity

```{r}
G2 <-  ggplot(Candidates, aes(x = total_nature_mean, y = Tempcont)) +
  geom_point(aes(color = habitat), alpha = 0.5) +
  theme_bw() +
  labs(y = "Number of years with same land use", x = "Average proportion of nature")

ggplotly(G2)
```

## Map Candidates

```{r}
labels <- paste(
    "<strong>Habitat: </strong>", Candidates$habitat,"<br>", "<strong>Species richness: </strong>", Candidates$sp_richness,"<br>", "<strong>Patch size: </strong>", Candidates$Patch_Size,"<br>", "<strong>Temporal continuity: </strong>", Candidates$Tempcont,"<br>") %>%
    lapply(htmltools::HTML)

pal <- colorBin(
  palette = "viridis",
  domain = Candidates$total_nature_mean
)

l <- leaflet(data = Candidates) 
esri <- c(Esri.WorldImagery = "Esri.WorldImagery", Esri.WorldStreetMap = "Esri.WorldStreetMap", Esri.WorldTopoMap = "Esri.WorldTopoMap", 
 Esri.WorldTerrain = "Esri.WorldTerrain")
for (provider in esri) {
  l <- l %>% addProviderTiles(provider, group = provider, options = providerTileOptions(minZoom = 1, maxZoom = 100))
}
l <- l %>%
  addLayersControl(baseGroups = names(esri),
    options = layersControlOptions(collapsed = TRUE))  %>%
  htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      myMap.on('baselayerchange',
        function (e) {
          myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
        })
    }") 

l %>% 
  addCircleMarkers(data = Candidates, color = ~pal(total_nature_mean), popup = ~labels, label = ~labels) %>% 
  addLegend("bottomright", pal = pal, values = ~total_nature_mean,
    title = "Mean Nature Proportion",
    opacity = 1
   ) %>% addScaleBar() %>% addMeasure(position = "bottomleft", primaryLengthUnit = "meters", primaryAreaUnit = "hectares")
```


## Table

```{r}
library(DT)
Candidates %>%
  arrange(desc(total_nature_mean)) %>% 
  datatable(extensions = 'Buttons', filter = 'top', 
            options = list(dom = 'Blfrtip',
                           scrollX='400px',
                           scrollY='200px',
                           buttons = c('copy', 'csv', 'excel'),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))  %>%
    formatRound(columns=c("Patch_Size", "sp_richness", "total_nature_mean", "total_nature_cv",
"nature_dry_mean", "nature_dry_cv", "lake_mean", "lake_cv","forest_mean", "forest_cv", "agriculture_intensive_temporary_crops_mean", "agriculture_intensive_temporary_crops_cv", 
"agriculture_intensive_permanent_crops_mean",
"agriculture_intensive_permanent_crops_cv"), digits=3)

```


## Check for selection

* [Here](https://rpubs.com/derek_corcoran/Ecogenetics_Filters)
